---
title: "Brief instruoduction of massprocesser"
author:
- name: Xiaotao Shen PhD (https://www.shenxt.info/)
- affiliation: School of Medicine, Stanford University
  url: https://www.shenxt.info/
date: "Created on 2020-03-28 and updated on `r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: no
  pdf_document:
    toc: no
vignette: >
  %\VignetteIndexEntry{massprocesser_instruction}
  %\VignettePackage{massprocesser}
  % \VignetteEngine{knitr::rmarkdown}
  % \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  message = TRUE
)
```

***

## **Introduction**


*massprocesser* is a R package which is used to process raw metabolomics data.

Please install it via [github](https://github.com/tidymass/massprocesser).

```{r,eval=FALSE,warning=FALSE, message=FALSE,R.options="", cache=TRUE}
if(!require(devtools)){
  install.packages("devtools")
}
devtools::install_github("tidymass/massprocesser")
```

We use the demo data in `demoData` package to show how to use `massprocesser`. Link is here: [https://github.com/jaspershen/demoData/tree/master/inst/mzxml/POS](https://github.com/jaspershen/demoData/tree/master/inst/mzxml/POS)

***

## **Usage**

Please see the Help document page to get the instruction of `massprocesser`.

***

## **Need help?**


If you have any questions about `massprocesser`, please don’t hesitate to email me (shenxt@stanford.edu).

<i class="fa fa-weixin"></i> [shenzutao1990](https://www.shenxt.info/files/wechat_QR.jpg)

<i class="fa fa-envelope"></i> shenxt@stanford.edu

<i class="fa fa-twitter"></i> [Twitter](https://twitter.com/JasperShen1990)

<i class="fa fa-map-marker-alt"></i> [M339, Alway building, Cooper Lane, Palo Alto, CA 94304](https://www.google.com/maps/place/Alway+Building/@37.4322345,-122.1770883,17z/data=!3m1!4b1!4m5!3m4!1s0x808fa4d335c3be37:0x9057931f3b312c29!8m2!3d37.4322345!4d-122.1748996)
